Case Study: RNA-Seq Differential Analysis

### 2018-03-15 datasets/RNA-Seq/RNA-Seq.Rmd
Wording.

We use DESeq2 to test each gene for differential gene expression between the two cell types. We set the parameter `independentFiltering=FALSE` to skip the independent filtering step. This step would be redundant with some of the FDR control methods that use gene expression as an independent covariate to gain power.

>>>>

We use DESeq2 to test each gene for differential gene expression between the two cell types. We set the parameter `independentFiltering=FALSE` to skip the independent filtering step, as this step would be redundant with some of the FDR control methods that use gene expression as an independent covariate to increase power.
